MINOS Handover Plots

### 2024-09-23 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Additions to the income module to try get the split scaling working (failed). Also some minor changes to the model for the same purpose, and additional plots added to handovers to look at income quintiles

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    xlab('Year') +
    ylab('Absolute Change in SF-12 MCS') +
    theme_minimal()

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed', color=plot_colour) +
    geom_point(color=plot_colour) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Absolute Change in SF-12 MCS') +
    theme_minimal()

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed', color=plot_colour) +
    geom_point(color=plot_colour) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Absolute Change in SF-12 MCS') +
    theme_minimal()

@@

  p1 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_line(data = plot_data, aes(x = year, y = diff_SF_12, group = run_id), alpha = 0.2) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12 MCS') +
    theme_minimal()

@@

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    xlab('Year') +
    ylab('Change in SF-12 MCS') +
    theme_minimal() +
    guides(fill=guide_legend(title="Income Quintile"))

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in SF-12 MCS') +
    theme_minimal() +
    guides(fill=guide_legend(title="Income Quintile"))

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in SF-12 MCS') +
    theme_minimal() +
    guides(fill=guide_legend(title="Income Quintile"))

@@

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, color = income_quintile, fill = income_quintile)) +
      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
      geom_line(linetype = 'dashed') +
      geom_point(show.legend = FALSE) +
      geom_hline(yintercept = 0, linetype = 'dashed') +
      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
      xlab('Year') +
      ylab('Change in mean SF-12 MCS') +
      theme_minimal() +
      guides(fill=guide_legend(title="Income Quintile"),
             linetype=guide_legend(title="Income Quintile"),
             group=guide_legend(title="Income Quintile"),
             color=guide_legend(title="Income Quintile"))

@@

  plot_data_confint <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF12),
              margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
              lower_SF12 = mean_SF12_change - margin_SF12,
              upper_SF12 = mean_SF12_change + margin_SF12) %>%
    mutate(
      mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
      margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12)
    )

  # lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
  # upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)

@@

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    xlab('Year') +
    ylab('Change in SF-12 MCS') +
    theme_minimal() +
    guides(group=guide_legend(title="Num Priority Subgroups"))

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in SF-12 MCS') +
    theme_minimal() +
    guides(group=guide_legend(title="Num Priority Subgroups"))

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in SF-12 MCS') +
    theme_minimal() +
    guides(group=guide_legend(title="Num Priority Subgroups"))

@@

  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(name = "Income Quintile", 
                      values = c("red", "blue", "green", "orange", "purple")) +
    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
         subtitle = tit,
         x = "Year",
         y = "Difference in SF_12 MCS") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

@@

  p1 <- ggplot(data = plot_data, aes(x = year, y = MHR_diff)) +
    geom_point() +
    geom_line() +
    labs(title = "Difference in count of individuals at risk of mental health issues",
         subtitle = tit) +
    xlab('Year') +
    ylab('Count') +
    theme_minimal()

@@

  p2 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_prop_diff)) +
    geom_point() +
    geom_line() +
    labs(title = "Difference in proportion of individuals at risk of mental health issues",
         subtitle = tit) +
    xlab('Year') +
    ylab('Percentage') +
    theme_minimal()

@@

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
      geom_line(linetype = 'dashed') +
      geom_point() +
      geom_hline(yintercept = 0, linetype = 'dashed') +
      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
      labs(title = 'Treated Population',
           subtitle = 'SF_12') +
      xlab('Year') +
      ylab('Change in mean SF-12 MCS')

@@

  p4 <- ggplot(plot_data_confint, aes(x = year, y = mean_hh_income_change)) +
      geom_ribbon(aes(ymin = lower_hh_income, ymax = upper_hh_income), linetype = 'dotted', alpha = 0.3) +
      geom_line(linetype = 'dashed') +
      geom_point() +
      geom_hline(yintercept = 0, linetype = 'dashed') +
      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
      labs(title = 'Treatment on the Treated',
           subtitle = 'Household Income') +
      xlab('Year') +
      ylab('Change in mean Household Income')

@@

@@

```{r}
SF12_change_income_quint(summary_group = 'families',
                                    scen.list = scen.list)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen)

SF12_change_income_quint2_fudged(summary_group = 'families',
                                    scen = scen)
```

>>>>

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal()

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed', color=plot_colour) +
    geom_point(color=plot_colour) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal()

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed', color=plot_colour) +
    geom_point(color=plot_colour) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal()

@@

  p1 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_line(data = plot_data, aes(x = year, y = diff_SF_12, group = run_id), alpha = 0.2) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal()

@@

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal() +
    guides(fill=guide_legend(title="Income Quintile"))

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal() +
    guides(fill=guide_legend(title="Income Quintile"))

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal() +
    guides(fill=guide_legend(title="Income Quintile"))

@@

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, color = income_quintile, fill = income_quintile)) +
      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
      geom_line(linetype = 'dashed') +
      geom_point(show.legend = FALSE) +
      geom_hline(yintercept = 0, linetype = 'dashed') +
      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
      xlab('Year') +
      ylab('Change in Mean SF-12 MCS') +
      theme_minimal() +
      guides(fill=guide_legend(title="Income Quintile"),
             linetype=guide_legend(title="Income Quintile"),
             group=guide_legend(title="Income Quintile"),
             color=guide_legend(title="Income Quintile"))

@@

  plot_data_confint <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF12),
              margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
              lower_SF12 = mean_SF12_change - margin_SF12,
              upper_SF12 = mean_SF12_change + margin_SF12) %>%
    mutate(
      mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
      lower_SF12 = mean_SF12_change - margin_SF12,
      upper_SF12 = mean_SF12_change + margin_SF12
    )

  # margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12)
  # lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
  # upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)

@@

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal() +
    guides(group=guide_legend(title="Num Priority Subgroups"))

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal() +
    guides(group=guide_legend(title="Num Priority Subgroups"))

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal() +
    guides(group=guide_legend(title="Num Priority Subgroups"))

@@

  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(name = "Income Quintile", 
                      values = c("red", "blue", "green", "orange", "purple")) +
    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
         subtitle = tit,
         x = "Year",
         y = "Change in Mean SF-12 MCS") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

@@

  p1 <- ggplot(data = plot_data, aes(x = year, y = MHR_diff)) +
    geom_point() +
    geom_line() +
    xlab('Year') +
    ylab('Count Change') +
    theme_minimal()

@@

  p2 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_prop_diff)) +
    geom_point() +
    geom_line() +
    xlab('Year') +
    ylab('Percentage Change') +
    theme_minimal()

@@

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
      geom_line(linetype = 'dashed') +
      geom_point() +
      geom_hline(yintercept = 0, linetype = 'dashed') +
      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
      labs(title = 'Treated Population',
           subtitle = 'SF_12') +
      xlab('Year') +
      ylab('Change in Mean SF-12 MCS')

@@

  p4 <- ggplot(plot_data_confint, aes(x = year, y = mean_hh_income_change)) +
      geom_ribbon(aes(ymin = lower_hh_income, ymax = upper_hh_income), linetype = 'dotted', alpha = 0.3) +
      geom_line(linetype = 'dashed') +
      geom_point() +
      geom_hline(yintercept = 0, linetype = 'dashed') +
      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
      labs(title = 'Treatment on the Treated',
           subtitle = 'Household Income') +
      xlab('Year') +
      ylab('Change in Mean Household Income')

@@

# SAMPLE STATISTICS

# data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
# data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
# 
# nrow(data)
# 
# 
# 5463300
# 
# 4580000
# 
# 
# 359328 / 458000 * 100
# 
# 100 / 78.4559
# 
# 
# 109338 * 12.74601

@@

```{r}
SF12_change_income_quint(summary_group = 'families',
                                    scen.list = scen.list)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen)
SF12_change_income_quint2_fudged(summary_group = 'families',
                                    scen = scen)
```

### 2024-09-23 minos/validation/handovers.Rmd
Additions to the income module to try get the split scaling working (failed). Also some minor changes to the model for the same purpose, and additional plots added to handovers to look at income quintiles

@@

ggplot(combined, aes(x = time, y = proportion, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_col() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')
```

@@

>>>>

## Income Quintile

```{r}
raw.dat <- raw.dat %>%
  group_by(time) %>%
  mutate(income_quint = ntile(hh_income, 5))

base.dat <- base.dat %>%
  group_by(time) %>%
  mutate(income_quint = ntile(hh_income, 5))
```

@@

ggplot(combined, aes(x = time, y = proportion, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_col() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')

rm(raw.hh_kids_prop, base.hh_kids_prop, combined)
```

@@

### Analysis by Quintile

```{r}
density_plot_quintile <- function(raw, base, quintile) {

  raw <- raw %>%
    filter(income_quint == quintile) %>%
    select(pidp, time, hh_income) %>%
    rename(Final_US = hh_income)
  base <- base %>%
    filter(income_quint == quintile) %>%
    select(pidp, time, hh_income) %>%
    rename(Baseline = hh_income)

  #combined <- merge(base, int, by = c('pidp', 'time'))

  combined <- rbind(raw, base)

  combined <- combined %>%
    pivot_longer(cols = Final_US:Baseline,
                 names_to = 'Source',
                 values_to = 'hh_income')

  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
    geom_density_ridges(alpha = 0.3) +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))

  return(p)
}

density_plot_quintile(base.dat, int.dat, quintile = 1)
density_plot_quintile(base.dat, int.dat, quintile = 2)
density_plot_quintile(base.dat, int.dat, quintile = 3)
density_plot_quintile(base.dat, int.dat, quintile = 4)
density_plot_quintile(base.dat, int.dat, quintile = 5)
```

#### Mean Income

```{r}
mean_income_quintile <- function(raw, base) {
  raw <- raw %>%
    select(pidp, time, hh_income, income_quint, weight) %>%
    mutate(source = 'Final_US')
  base <- base %>%
    select(pidp, time, hh_income, income_quint, weight) %>%
    mutate(source = 'Baseline')

  combined <- rbind(base, int)

  combined <- combined %>%
    group_by(time, income_quint, source) %>%
    summarise(mean = weighted.mean(hh_income, weight),
              median = weighted.median(hh_income, weight))

  combined$income_quint <- factor(combined$income_quint)
  combined$source <- factor(combined$source)

  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Mean hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Median hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  print(p1)
  print(p2)
  #return(p)
}

mean_income_quintile(base.dat, int.dat)
```

#### Thresholds Over Time

```{r}
# get min-max by group as this is upper and lower limits of the quintiles

base <- base.dat %>%
  group_by(time, income_quint) %>%
  summarise(min = min(hh_income),
            max = max(hh_income)) %>%
  mutate(source = 'Baseline')
int <- int.dat %>%
  group_by(time, income_quint) %>%
  summarise(min = min(hh_income),
            max = max(hh_income)) %>%
  mutate(source = 'Intervention')

combined <- rbind(base, int)
combined$income_quint <- factor(combined$income_quint)

quintile_threshold_plot <- function(data, year) {
  ggplot(filter(data, time == year), 
         aes(x = income_quint, y = min,
             ymin = min, lower = min, ymax = max, upper = max,
             group = source, 
             colour = source, 
             fill = source)) +
    geom_crossbar(position = position_dodge()) +
    labs(title = 'Quintile Thresholds',
         subtitle = year)
}

quintile_threshold_plot(combined, year = 2020)
quintile_threshold_plot(combined, year = 2021)
quintile_threshold_plot(combined, year = 2025)
quintile_threshold_plot(combined, year = 2030)
quintile_threshold_plot(combined, year = 2035)
```
